Investigating Neolithic pottery usage in the Yanyuan Basin in Southwest China using organic residue analysis

### 2022-11-30 analysis/paper/paper.Rmd
added the code chunk for chromatogram

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300)
```

@@

```{r tidy data}
library(tidyverse)

@@

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300)

image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
```

@@

```{r tidy-data}
library(tidyverse)

@@

```{r highlight-compounds}
# highlight target compounds
highlight_GJB_four <-
  meth_all %>%
  mutate(retention = round(Path, 1)) %>%
  group_by(sample, retention) %>%
  arrange(desc(File)) %>%
  distinct(retention, .keep_all = TRUE) %>%
  mutate(FA = case_when(
    retention == 21.6 ~ "C14:0",
    retention == 23.6 ~ "C15:0",
    retention == 25.5 ~ "C16:0",
    retention == 27.3 ~ "C17:0",
    retention == 28.4 ~ "C18:1",
    retention == 29.1 ~ "C18:0",
    retention == 32.4 ~ "C20:0",
    retention == 35.4 ~ "C22:0")) %>%
  filter(name %in% c("SYG-3", "SYG-TN13-E22-2#1", "SYG-TN13-E22-1", "SYG-TN13-E23-3")) %>%
  filter(File > 100000)

highlight_IS <-
  meth_all %>%
  mutate(retention = round(Path, 1)) %>%
  group_by(sample, retention) %>%
  arrange(desc(File)) %>%
  distinct(retention, .keep_all = TRUE) %>%
  mutate(FA = case_when(
    retention == 33.9 ~ "IS",
    retention == 41.3 ~ "IS")) %>%
  filter(name %in% c("SYG-3", "SYG-TN13-E22-2#1", "SYG-TN13-E22-1", "SYG-TN13-E23-3"))

# highlight the compounds in the potsherd with high concentration
highlight_SYG2_2 <-
  meth_all %>%
  mutate(retention = round(Path, 1)) %>%
  group_by(sample, retention) %>%
  arrange(desc(File)) %>%
  distinct(retention, .keep_all = TRUE) %>%
  mutate(FA = case_when(
    retention == 21.6 ~ "C14:0",
    retention == 25.5 ~ "C16:0",
    retention == 27.3 ~ "C17:0",
    retention == 28.4 ~ "C18:1",
    retention == 29.1 ~ "C18:0",
    retention == 31.0 ~ "C19:0",
    retention == 32.4 ~ "C20:0",
    retention == 35.4 ~ "C22:0",
    retention == 36.8 ~ "C23:0",
    retention == 38.2 ~ "C24:0",
    retention == 40.9 ~ "C26:0",
    retention == 33.9 ~ "IS",
    retention == 41.3 ~ "IS",
    retention == 45.6 ~ "C:30",
    retention == 47.8 ~ "C:32")) %>%
  filter(name == "SYG-TN13-E22-2#2")
```

```{r chromatogram-four}
# plot the first four
chroma_four <-
  meth_all %>%
  filter(name %in% c("SYG-3", "SYG-TN13-E22-2#1", "SYG-TN13-E22-1", "SYG-TN13-E23-3")) %>%
  mutate(File = ifelse(File > 550000, 550000, File)) %>%
  ggplot(aes(Path, File)) +
  geom_line(size = 0.3) +
  geom_text(data = highlight_GJB_four, #ggrepel::geom_text_repel
            aes(label = FA, angle = 90),
            size = 3,
            nudge_y = 87000,
            show.legend = FALSE) +
  geom_text(data = highlight_IS,
            aes(label = FA),
            size = 3,
            nudge_y = 40000,
            show.legend = FALSE) +
  geom_segment(aes(x= 41.1, xend= 41.5, y= 550000, yend= 550000), size =0.3) +
  geom_segment(aes(x= 41.1, xend= 41.5, y= 560000, yend= 560000), size =0.3) +
  annotate("text", x = 41.3, y = 600000, label = "IS", size =3) +
  facet_wrap(~name, ncol = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, 600000),
                     breaks = seq(0, 600000, 200000)) +
  scale_x_continuous(limits = c(20, 45),
                     expand = c(0, 0.5)) + # don't log, many peaks and distort real counts
  labs(x = "retention time", y = "Relative Intensity") +
  theme_minimal()

ggsave(plot = chroma_four,
       here::here("analysis","figures", "chromatograms_four.png"),
       width = 8,
       height = 8,
       dpi = 300,
       units = "in")
```

```{r chromatograms-plots-four, echo=FALSE, fig.cap= "chromatograms"}
knitr::include_graphics(here::here("analysis/figures/chromatograms_four.png"))
```
